Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-16 automatica/paper.tex
fixes

During any given ADC conversion, the continuous signal will be sampled in
the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
(x)$ (assuming the ADC discretization is the same as the digital
implementation).  This sampling uses a threshold which is defined by the
less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
of the ADC and some non-linearities of the circuitry.  The overall conversion is
%
$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(y(t)) = y_k :
y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
%
If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
and $n$ is the sampling time and $k$ the number of steps, then we may define
some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.

As stated before, we assume that the domain of the
ADC is that of the digital controller (i.e, the quantizer includes any
digital gain added in the code).  The process of quantization in the DAC is
similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
resolution in higher than the ADCs, then the DAC quantization error is equal
to zero.  From the above equations we can now define the ADC and DAC
quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
$q_2=q_\mathit{dac}$.  This is illustrated in
Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
whether the noise is correlated, hence we may use them to over-approximate
the noise effect on the state space progression over time.  The
resulting dynamics are
%
\begin{align*}
%\label{eq:pre_quantization}
{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
\end{align*}
%
which result in the following closed-loop dynamics:
%
\begin{align*}
%\label{eq:quantization}
{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
\end{align*}

@@

This induces two types of the errors detailed above: first, the truncation
error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
\rangle}(x_{k})$; and second, the rounding error introduced by the
multiplication operation.  We represent these errors as non-deterministic
additive noise.

>>>>

During any given ADC conversion, the continuous signal will be sampled in
the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
(x)$ (assuming the ADC discretization is the same as the digital
implementation).  This sampling uses a threshold which is defined by the
less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
of the ADC and some non-linearities of the circuitry.  The overall conversion is
%
$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(y(t)) = y_k :
y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
%
\note{what is signal y here? how are these formulae related to those in the section on the AA-based back-end?}
If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
and $n$ is the sampling time and $k$ the number of steps, then we may define
some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.

As stated before, we assume that the domain of the
ADC is that of the digital controller (i.e, the quantizer includes any
digital gain added in the code).  The process of quantization in the DAC is
similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
resolution in higher than the ADC, then the DAC quantization error is equal
to zero.  From the above equations we can now define the ADC and DAC
quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
$q_2=q_\mathit{dac}$.  This is illustrated in
Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
whether the noise is correlated, hence we may use them to over-approximate
the noise effect on the state space progression over time.  The
resulting dynamics are
%
\begin{align*}
%\label{eq:pre_quantization}
{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
\end{align*}
%
which result in the following closed-loop dynamics:
%
\begin{align*}
%\label{eq:quantization}
{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
\end{align*}

@@

This induces two types of the errors detailed above: first, the truncation
error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
\rangle}(x_{k})$; and second, the rounding error introduced by the
multiplication operation.  
\note{ We represent these errors as non-deterministic
additive noise. }
